First, I dedicate this milestone to my family. To my sister Alexya Lemos, for the memorable moments of joy and fun -- it is always fun to
discuss and brainstorm with you insights about whatever we happen to be watching together.

To my father Rodolfo Rocha, for sharing with me his wise and insightful perceptions about life.
Your distinct perspectives bring me awareness about any subject that we end up
discussing. Not everyone can have the luxuary of having
civil and calm conversations with whom they may fundamentally disagree. My dad gave me my first
opportunities of this kind and I'm truly grateful to him for that.

And foremost, to my mother Dania Lemos. Since my infancy, my mom has been a fundamental pillar in my life;
from my first pronounced word, to my reading and writing, and later in the first years of school; she has most if not
all of the merit in regards to those accomplishments. The move from school to university required way more effort
from me and my mom came along for the ride: she became my golden guardian. My countless unhealthy decisions in the pursuit
of doing the best in my academic journey were counter-balanced by her always-present joyful smiles and help in whatever
she should offer me. Further, she kept celebrating any of my achievements, regardless of how minor or major, to make me
believe in a self-esteem based on merit and high effort. Later on, after I started getting into the software industry
as a Software Developer, all my complements about my english I redirected to my mom -- and that is because she deserves
all the attention and merit about this skill that today is a must-have in my life. Without her there to keep me going
on learning a foreign language, I would not be where I am today, far from it. Dania is the inspirational example that every
person needs: an unstoppable warrior for us to follow; one based on kindness, effort, goodness, and ambition. Let your Will
be charged by hers; let your Heart by melted by hers; your paramount goal should be learn from her and be considerate on what
she has to say and share with you.

Second, I dedicate this work to my close friends -- Edil Medeiros, Marcos Magueta, Mário Junior, Elisama Honesko, Gabriela Lul and others. Thank you for
all the great conversations, insights, and fun memories. I'm truly grateful for all of you either by helping me improve in all
fronts or by having faith I could produce a great thesis, or both.
